\textbf{\hmwkTitle} \\ \smallskip \normalsize{\hmwkSubtitle} \\ \hmwkClass \\ \normalsize{\hmwkClassInstructor} \\

### 2017-05-18 paper/main.tex
changed minor formatting details in report

\PassOptionsToPackage{numbers, compress}{natbib}
\usepackage{url}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{mathtools}
\usepackage{fancyvrb}
\usepackage{array,booktabs,calc,blindtext}
% \usepackage[shortlabels]{enumerate}

@@

\newcommand{\hmwkTitle}{Extensible Physics Engine}
% \newcommand{\hmwkIssueDate}{22 February 2017}
%\newcommand{\hmwkDueDate}{8 May 2017}
\newcommand{\hmwkClass}{6.905/6.945 Final Project Draft}
% \newcommand{\hmwkClassInstructor}{Professor Gerry Sussman}
\newcommand{\hmwkAuthorName}{\textbf{Michael Chang, Abigail Choe, Leon Shen}}

\title{
    \textmd{\hmwkClass:\ \hmwkTitle}\\
    % \normalsize{\hmwkClassInstructor}\\
    % \small{Issued\ on\ \hmwkIssueDate}\\
    %\small{Due\ on\ \hmwkDueDate}
}
\author{\hmwkAuthorName}
\date{}
\begin{document}
\maketitle
\section{Introduction}

@@

% internal NOTE: generic procedures--we haven't actually used them in the code yet!

@@

\begin{figure}[h!]
  \centering
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figs/gravity.png}
  \caption{[\textit{left}] \texttt{earth-moon}; [\textit{center}] \texttt{binary-stars}; [\textit{right}] \texttt{solar-system}}
  \label{figure:gravity}
\end{figure}

@@

\begin{figure}[h!]
  \centering
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{figs/charges.png}
  \caption{[\textit{left}] \texttt{charges-1}; [\textit{center}] \texttt{charges-2}; [\textit{right}] \texttt{charged-solar-system}}
  \label{figure:charges}
\end{figure}

>>>>

\PassOptionsToPackage{numbers, compress}{natbib}
\usepackage{url}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{mathtools}
\usepackage{fancyvrb}
\usepackage{array,booktabs,calc,blindtext}

@@

\newcommand{\hmwkTitle}{Extensible Physics Engine}
\newcommand{\hmwkSubtitle}{Final Project Report}
\newcommand{\hmwkClass}{6.905/6.945 - Spring 2017}
\newcommand{\hmwkClassInstructor}{Professor Gerald Sussman}
\newcommand{\hmwkAuthorName}{\textbf{Michael Chang, Abigail Choe, Leon Shen}}

\title{
    \textbf{\hmwkTitle} \\
    \smallskip
    \normalsize{\hmwkSubtitle} \\
    \hmwkClass \\
    \normalsize{\hmwkClassInstructor} \\
}
\author{\hmwkAuthorName}
\date{}
\begin{document}
\maketitle
\section{Introduction}

@@

% internal NOTE: generic procedures--we haven't actually used them in the code
%                yet!

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]
    {figs/gravity.png}
  \caption{[\textit{left}] \texttt{earth-moon}; [\textit{center}]
    \texttt{binary-stars}; [\textit{right}] \texttt{solar-system}}
  \label{figure:gravity}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]
    {figs/charges.png}
  \caption{[\textit{left}] \texttt{charges-1};
    [\textit{center}] \texttt{charges-2};
    [\textit{right}] \texttt{charged-solar-system}}
  \label{figure:charges}
\end{figure}
